---
title: "quantum compute"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{quantum compute}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Intriducing the quantum compute package

a few words about your motivation in writing this R package. What is it meant for, to do and what data does it work with?

## Installation Intructions
```{r setup}
devtools::install_github("sfontenot/Project_three")
library(quantum)
```

## Where to get the data
+ could use google sheets and give people intructions for that 
+ can stash data in an R package

## Using Function One

```{r warning=FALSE}

quantum::clean()

```
+This Function uses one argument and that is simply a file path. This will clean your data and also change the characters to factors. 


## Using function Two and getting data less than 5
```{r}
quantum::bubble()

```

## Using Function Three and looking at the season relationship to Butterflies

```{r}

quantum::seasons()
```


## Using Function Four
```{r}

quantum::ANOVA()
```
## Using Function Five

```{r}
quantum::plot()
```
